Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-23 article.tex
put in evidence the stationary ot the stochastic process

Let us model the fluorescence indicators of all $p$ neurons as a set of random
variables $X = \{X_1, \dots, X_p\}$ following a joint probability distribution
$P_X$. In the statistical framework, two random variables $X_i$ and $X_j$ are
said to be conditionally independent to a (possibly empty) set of controlling
random variables $Z$, denoted $X_i \perp X_j | Z$, if the joint conditional
probability distribution $P_{X_i, X_j | Z}$ factorizes into $P_{X_i|Z}
P_{X_j|Z}$. In particular, when $X_i$ and $X_j$ are conditionally independent
with respect to all the other variables, denoted $X_i \perp X_j | X^{-i,j}$,
then the observation of $X_i$ given the knowledge of $X^{-i,j}$ provides no
information about $X_j$, and vice-versa. From a graphical point of view and
assuming no hidden variable, this indicates that $X_i$ and $X_j$ do not
directly interact (i.e., $(i,j) \notin E$). By opposition, if $X_i$ and $X_j$
are conditionally dependent with respect to all other variables, denoted $X_i
\not\perp X_j | X^{-i,j}$, then the observation of one of the two variables
provides some information about the other, therefore highlighting a direct
interaction between the two random variables (i.e., $(i, j) \in E$).

>>>>

Let us model the fluorescence concentration of all $p$ neurons as a set of random
variables $X = \{X_1, \dots, X_p\}$ following a joint probability distribution
$P_X$, a stationary stochastic process.
In the statistical framework, two random variables $X_i$ and $X_j$ are
said to be conditionally independent to a (possibly empty) set of controlling
random variables $Z$, denoted $X_i \perp X_j | Z$, if the joint conditional
probability distribution $P_{X_i, X_j | Z}$ factorizes into $P_{X_i|Z}
P_{X_j|Z}$. In particular, when $X_i$ and $X_j$ are conditionally independent
with respect to all the other variables, denoted $X_i \perp X_j | X^{-i,j}$,
then the observation of $X_i$ given the knowledge of $X^{-i,j}$ provides no
information about $X_j$, and vice-versa. From a graphical point of view and
assuming no hidden variable, this indicates that $X_i$ and $X_j$ do not
directly interact (i.e., $(i,j) \notin E$). By opposition, if $X_i$ and $X_j$
are conditionally dependent with respect to all other variables, denoted $X_i
\not\perp X_j | X^{-i,j}$, then the observation of one of the two variables
provides some information about the other, therefore highlighting a direct
interaction between the two random variables (i.e., $(i, j) \in E$).
